LAGOS lake depth

### 2020-11-25 manuscript/si_template_2019.tex
fix table S1 variable names

% source at tables/01_predictors.Rmd
\begin{table}
\caption{Summary of lake characteristics for the present study (and for lakes in the contiguous United States). Predictor variables for computing random forest offsets (Equation 2) are printed in bold face. Dashes (-) indicate an identical sample size among this study and that of the contiguous United States.} \label{tableS1}
\centering
\setlength\tabcolsep{1.5pt} % default value: 6pt

\begin{tabular}{lllll}
\hline
Variable & Median & Q25 & Q75 & n\\
\hline
\textbf{Area (ha)} & 55 (33) & 21 (11) & 140 (100) & 4820 (17700)\\
\textbf{Island area (ha)} & 0 (0) & 0 (0) & 0.18 (0.076) & 4820 (17700)\\
- & 1500 (1100) & 880 (640) & 2500 (2200) & 4820 (17700)\\
- & 91 (88) & 41 (40) & 140 (140) & 4820 (17700)\\
- & 710 (560) & 430 (320) & 1200 (1000) & 4820 (17700)\\
- & 380 (290) & 230 (170) & 610 (500) & 4820 (17700)\\
- & 0 (0) & 0 (0) & 58 (25) & 4820 (17700)\\
- & 0 (0) & 0 (0) & 3 (3) & 4820 (17700)\\
- & 0 (0) & 0 (0) & 1 (1) & 4820 (17700)\\
- & 26000 (27000) & 23000 (23000) & 27000 (38000) & 4820 (17700)\\
\textbf{Deepest point distance (m)} & 180 (-) & 110 (-) & 290 (-) & 4820 (-)\\
\textbf{Visual center distance (m)} & 240 (-) & 160 (-) & 390 (-) & 4820 (-)\\
- & 0.046 (-) & 0.024 (-) & 0.079 (-) & 4820 (-)\\

- & 0.062 (-) & 0.029 (-) & 0.14 (-) & 4800 (-)\\

- & 0.077 (-) & 0.051 (-) & 0.11 (-) & 4820 (-)\\

- & 0.077 (-) & 0.038 (-) & 0.13 (-) & 4590 (-)\\

- & 0.077 (-) & 0.037 (-) & 0.13 (-) & 4540 (-)\\
\hline
\end{tabular}
\end{table}

>>>>

% source at tables/01_predictors.Rmd
\begin{table}
\caption{Summary of lake characteristics for the present study (and for lakes in the contiguous United States). Predictor variables for computing random forest offsets (Equation 2) are printed in bold face. Dashes (-) indicate an identical sample size among this study and that of the contiguous United States.} \label{tableS1}
\centering
\setlength\tabcolsep{1.5pt} % default value: 6pt
\begin{tabular}{lllll}
\hline
Variable & Median & Q25 & Q75 & n\\
\hline
Max depth (m) & 8.2 (7) & 4.6 (3.7) & 14 (12) & 4820 (17700)\\
\textbf{\textbf{Perimeter (m)}} & 4400 (3500) & 2500 (1800) & 8100 (7300) & 4820 (17700)\\
\textbf{\textbf{Shoreline development}} & 1.7 (1.7) & 1.4 (1.4) & 2.1 (2.2) & 4820 (17700)\\
\textbf{\textbf{Elevation (m)}} & 300 (340) & 180 (210) & 400 (460) & 4820 (17700)\\
\textbf{\textbf{Watershed-lake ratio}} & 7.8 (10) & 3.8 (4.4) & 17 (29) & 4820 (17700)\\
\textbf{\textbf{Deepest point distance (m)}} & 180 (-) & 110 (-) & 290 (-) & 4820 (-)\\
\textbf{\textbf{Mean deepest point distance (m)}} & 140 (-) & 87 (-) & 230 (-) & 4820 (-)\\
\textbf{\textbf{Visual center distance (m)}} & 240 (-) & 160 (-) & 390 (-) & 4820 (-)\\
Mean inlake slope (m/m) & 0.043 (-) & 0.021 (-) & 0.09 (-) & 4820 (-)\\
Inlake slope online (m/m) & 0.062 (-) & 0.029 (-) & 0.14 (-) & 4800 (-)\\
Inlake slope (m/m) & 0.046 (-) & 0.024 (-) & 0.079 (-) & 4820 (-)\\
Inlake slopes (m/m) & 0.057 (-) & 0.032 (-) & 0.098 (-) & 4820 (-)\\
Inlake slopes online (m/m) & 0.07 (-) & 0.034 (-) & 0.15 (-) & 4800 (-)\\
Nearshore mean slope (m/m) & 0.077 (-) & 0.051 (-) & 0.11 (-) & 4820 (-)\\
Nearshore slope online (m/m) & 0.077 (-) & 0.038 (-) & 0.13 (-) & 4590 (-)\\
Nearshore slopes online (m/m) & 0.077 (-) & 0.037 (-) & 0.13 (-) & 4540 (-)\\
\hline
\end{tabular}
\end{table}

### 2020-11-25 tables/01_predictors.Rmd
fix table S1 variable names

# setwd("tables")
nearshore <- read.csv("../data/00_geometry/nearshore.csv", 
                      stringsAsFactors = FALSE) %>%
  dplyr::select(llid, contains(c("slope_mean", "slope_online_mean", 
                                 "slopes_mean", "slopes_online_mean")))
dt_all <- read.csv("../data/lagosus_depth_predictors.csv", 
               stringsAsFactors = FALSE) %>%
  distinct(lagoslakeid, .keep_all = TRUE) %>%
  dplyr::select(-inlake_slope_mean)
dt_bathy <- dt_all %>%
  right_join(nearshore, by = c("lagoslakeid" = "llid")) %>%
  dplyr::select(-contains("lagoslakeid"), 
                -contains("lake_nhd"), 
                -contains("lake_huc"))

@@

```{r predictors_table}
# setwd("figures")
slope_distance_vars <- unique(dt_combined$variable)[
  stringr::str_detect(unique(dt_combined$variable), 
                     "dist_|e_slope_|dists_|e_slopes")]
exclude_vars <- unique(dt_combined$variable)[
  stringr::str_detect(unique(dt_combined$variable), 
                     "totalarea|islandperimeter|between|buffer100m|lake_meandepth_m")]

dt <- dt_combined %>%
  dplyr::filter(str_detect(variable, 
                c(paste0(slope_distance_vars, collapse = "|"),
                  "^lake_|^ws_lake_arearatio"))) %>%
  dplyr::filter(!str_detect(variable,
                            paste0(exclude_vars, collapse = "|")))
                       # %>%
  # mutate(n = dt_bathy$n[which(dt_bathy$variable == "inlake_slope")])

@@

@@

# clipr::write_clip(
#   knitr::kable(dt, format = 'latex', align = c("lllll"), escape = FALSE))
```

>>>>

# setwd("tables")
nearshore <- read.csv("../data/00_geometry/nearshore.csv", 
                      stringsAsFactors = FALSE) %>%
  dplyr::select(llid, contains(c("slope_mean", "slope_online_mean", 
                                 "slopes_mean", "slopes_online_mean")))
dt_all <- read.csv("../data/lagosus_depth_predictors.csv", 
               stringsAsFactors = FALSE) %>%
  distinct(lagoslakeid, .keep_all = TRUE) %>%
  dplyr::select(-matches("inlake_slopes_online"), 
                -matches("inlake_slope_online"), 
                -matches("inlake_slope_mean"),
                -lake_centroidstate.y, 
                -lake_centroidstate.x)
dt_bathy <- dt_all %>%
  right_join(nearshore, by = c("lagoslakeid" = "llid")) %>%
  dplyr::select(-contains("lagoslakeid"), 
                -contains("lake_nhd"), 
                -contains("lake_huc"))

@@

```{r predictors_table}
# setwd("figures")
# dt_combined$variable
exclude_vars <- unique(dt_combined$variable)[
  stringr::str_detect(unique(dt_combined$variable), 
                     "totalarea|islandperimeter|between|buffer100m|lake_meandepth_m|countyfips|upstream|length_m|width_m|orientation_deg|nws_")]
slope_distance_vars <- unique(dt_combined$variable)[
  stringr::str_detect(unique(dt_combined$variable), 
                     "dist_|e_slope_|dists_|e_slopes")]
slope_distance_vars <- slope_distance_vars[!slope_distance_vars %in% exclude_vars]

dt <- dt_combined %>%
  dplyr::filter(variable %in% c(slope_distance_vars, 
                           "lake_maxdepth_m", "lake_elevation_m",
                           "lake_perimeter_m", "lake_shorelinedevfactor",
                           "ws_lake_arearatio"))
dt$variable
                       # %>%
  # mutate(n = dt_bathy$n[which(dt_bathy$variable == "inlake_slope")])

@@

# dt$variable[!dt$variable %in% taxonomy_key$col_name]

dt[9:16,] <- dplyr::arrange(dt[9:16,], variable)

@@

# clipr::write_clip(
#   gsub("%\\*\\*", "\\\\%\\*\\*",
#   gsub("_", "\\\\_",
#   gsub("%\\\\", "\\\\%\\\\",
#   sub("\\\\midrule", "\\\\hline",
#   sub("\\\\bottomrule", "\\\\hline",
#   sub("\\\\toprule", "\\\\hline",
#       knitr::kable(dt, digits = 2, format = "latex",
#      booktabs = TRUE, linesep = "", align = c("l"), escape = FALSE)))))))
#    )
```
